%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {FIS Site Reliability Engineer} % Job title
    {Hapag-Lloyd AG} % Organization
    {Gdańsk, Poland} % Location
    {Mar. 2025 --- Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Modernized legacy workflows:} Replaced GUI-driven deployment processes for mainframe-hosted Freight Information System (FIS) applications with Bash-based automation via UrbanCode Deploy, significantly improving maintainability.
        \item \textbf{Enhanced system observability:} Troubleshot production reliability issues across distributed and legacy infrastructure using Datadog, Grafana, and ELK stack for deep log analysis and operational visibility.
        \item \textbf{Collaborative CI/CD support:} Maintained and optimized critical operational workflows using Jenkins and GitLab in close alignment with development and platform teams.
        \item \textbf{Cross-functional alignment:} Collaborated across development, database, and observability squads to support high-availability customer shipping and booking systems.  
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Infrastructure and DevOps Engineer} % Job title
    {Intel Technology Poland} % Organization
    {Gdańsk, Poland} % Location
    {Jul. 2022 --- Dec. 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Scalable CI Infrastructure:} Architected and configured hybrid (Linux/Windows) self-hosted GitHub Actions runners and CI workflows to automate build/test processes and maximize resource utilization.
        \item \textbf{Pipeline Security \& Stability:} Implemented Docker containerization across pipelines to ensure consistent environments and integrated Coverity static analysis gates to enforce code quality.
        \item \textbf{Knowledge Sharing \&  Docs:} Conducted technical training sessions on static analysis tools and CI/CD best practices while maintaining extensive documentation to accelerate team onboarding.   
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Software Development Intern} % Job title
    {Intel Technology Poland} % Organization
    {Gdańsk, Poland} % Location
    {Mar. 2020 --- Jun. 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Legacy Migration:} Successfully migrated over 30 source code repositories from TeamForge to GitHub while maintaining complete code integrity.
        \item \textbf{Build System Optimization:} Designed and maintained Jenkins CI pipelines, optimizing internal tool build systems to boost efficiency and reliability.
        \item \textbf{Team Enablement:} Conducted introductory Git/GitHub training sessions for development teams to improve version control adoption and contributed to internal tool development.
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
